--- 
title: "A `dplyr` tutorial"
author: "sn248"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: sn248/dplyr-tutorial
description: "This is a tutorial on the basics of R package dplyr."
---

# Preamble

\texttt{dplyr} is the next iteration of \texttt{plyr} package by Hadley Wickham. Much faster than the earlier \texttt{plyr} package, works on larger datasets. A crucial differerence is the use of pipe operator `%>%` to perform tasks in `dplyr`. Installation and use is same as other packages. (test)

```{r eval=FALSE}
devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need to install XeLaTeX.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
